Investigating social change during cultural contact period using geometric morphometry of pottery shapes from Iron Age northeastern Taiwan

### 2020-02-15 analysis/paper/paper.Rmd
fix two errors that prevented knitting

total_no <- sum(phase_fre$n)
pre_no <- phase_fre$n[1]
Euro_no <- phase_fre$n[2]
Chi_no <- phase_fre$n[3]
```

@@

```{r CV-test-PCs-table}
# CVs on shape PCs for standardization
pc1 <- data.frame(
x = op.p$x[,1],
y = as.character(op.p$fac$phase),
stringsAsFactors = F)

@@

```{r metricCVstest}
library(cvequality)
# read metric data
kwl_p_ave <- readr::read_csv(here("analysis", "data", "raw_data", "KWL-pottery-metrics-tidy-ave.csv"))
# number for each phase 
kwl_p_ave_total <-
  kwl_p_ave %>% 
  count(period)
# inline code
metric_all <- sum(kwl_p_ave_total$n)
pre <- kwl_p_ave_total$n[3]
euro <- kwl_p_ave_total$n[2]
chi <- kwl_p_ave_total$n[1]

>>>>

total_no <- sum(phase_fre$n)
pre_no <- phase_fre$n[1]
Euro_no <- phase_fre$n[2]
Chi_no <- phase_fre$n[3]

# read metric data
kwl_p_ave <- readr::read_csv(here("analysis", "data", "raw_data", "KWL-pottery-metrics-tidy-ave.csv"))

# number for each phase 
kwl_p_ave_total <-
  kwl_p_ave %>% 
  count(period)

# inline code later in the paper
metric_all <- sum(kwl_p_ave_total$n)
pre <- kwl_p_ave_total$n[3]
euro <- kwl_p_ave_total$n[2]
chi <- kwl_p_ave_total$n[1]
```

@@

```{r CV-test-PCs-table}
library(cvequality)
# CVs on shape PCs for standardization
pc1 <- data.frame(
x = op.p$x[,1],
y = as.character(op.p$fac$phase),
stringsAsFactors = F)

@@

```{r metricCVstest}
